---
title: "ESM 206 Lab 8"
author: "Logan Babcock"
date: "November 15, 2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# attache packages
library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)


# read in data

homes <- read_csv(here("data", "slo_homes.csv"))

```

# a little bit of cleaning:

Make a subset called homes_sub that only contains rows where the city is:
- slo,
- ag
- atascadero
-santa maria-orcutt

```{r eval = FALSE}
# use the eval = false if you dont want this code chunk to even run!
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))

```

# a bit of exploring!!

Find summary stats for home price based on city and sale status

- Find and return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status

```{r}

# make a summary table

summary_table <- homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price),
            sd_price = sd(Price))

# exploratory graph
ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) +# color and fill are in aes because they are referring to a variable! if its referring to a constant, should be outside aes
  scale_x_continuous(limits = c(0, 3e6))
```

Explore the relationship between square footage and home price

```{r}
ggplot(data = homes_sub, x= SqFt, y = Price) +
  geom_point(aes(x = SqFt, y = Price, color = City, shape = Status))
```

# model the relationship
using home price as the dependant variable

```{r}
# making a saturated model, uses every variable in dataset

homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub)

# make a subset with only swantitative variables

homes_quant <- homes_sub %>% 
  select(Price:PricePerSqFt)

# finding correlation between these
homes_cor <- cor(homes_quant)
homes_cor

corrplot(homes_cor)

# looking at the plotted linear model to double check assumptions
plot(homes_lm1)

```
# trying anohter model where we simplify it a bit:

making another model with just 
- city,
- sqft
- status
```{r}
# new model

homes_lm2 <- lm(Price ~ City + SqFt + Status, data = homes_sub)
homes_lm2

plot(homes_lm2)
```

## Find the AIC value of each model
```{r}
AIC(homes_lm1)
AIC(homes_lm2)
# not satisfied with these, will make another!
```

making a new model that ahs better fit, check out the fit and AIC

```{r}
homes_lm3 <-lm(Price ~ City + SqFt + Bedrooms + Status, data = homes_sub)
homes_lm3
plot(homes_lm3)
AIC(homes_lm3)

homes_lm4 <- lm(Price ~ City + SqFt, data = homes_sub)
homes_lm4
plot(homes_lm4)
AIC(homes_lm4)

# getting a model summary - if you do this for multiple models it wants the models as a list

modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

